Introduction to LLL\\``Cryptography''

### 2021-05-27 paper.tex
Implementation of RSA Attack for 1024 bit modulus

\[
    z = pad || m = 0x74686973206b65793a00 || m
\]

where $||$ is the concatenation.\\

@@

\[
    c = z^e \mod N = 0x8185d7de1d7cb8801e69c0bf
\]

@@

\begin{align*}
    f(x) = x^3 + 0x15d393c596142306bae000000x^2 + 0x969acdb25c5f7b5ff7f29bc59x \\
    + 0x75abf10edc37c4b90c5897322
\end{align*}

@@

\[
    \begin{split}
    v = (0x24409ad85f781X^3, -0xd75ab858b980X^2, \\
        0x1973847f4ddb8X, -0x9a2d87b43d)
    \end{split}
\]

@@

\[
    \begin{split}
        g(x) = 0x24409ad85f781x^3  - 0xd75ab858b980x^2 \\ 
        + 0x1973847f4ddb8x - 0x9a2d87b43d
    \end{split}
\]

@@

If we compute the root of $g(x)$ over the integers we obtain $m = 0x61$ which is the correct result.\\

If you want to find bigger root you need to create a bigger lattice with more polynomials generated with \ref{eq:create_pol},
this method is better described in TODO.

>>>>

\[
    z = pad || m = 0x74686973206b65793a || m
\]

where $||$ is the concatenation. The padding is the ascii encoding of ``this key:''\\

@@

\[
    c = z^e \mod N = 0x5b603cda4b72100c6f25954fc
\]

@@

\begin{align*}
    f(x) = x^3 + 0x15d393c596142306bae0000x^2 + 0x1b53c5e184a49b39f9ad9eedbx\\
    + 0x486a5d936fb568185c8ff0506
\end{align*}

@@

\[
    \begin{split}
    v = (0x90843131bc53X^3 + 0x2736f60b1c7ba3294X^2, \\
    -0x1bec331b20625341b6d73X, 0x47336b98335c143ac912ec9e)
    \end{split}
\]

@@

\[
    \begin{split}
        g(x) = 0x90843131bc53x^3 + 0x2736f60b1c7ba3294x^2 \\
        -0x1bec331b20625341b6d73x + 0x47336b98335c143ac912ec9e
    \end{split}
\]

@@

If we compute the root of $g(x)$ over the integers we obtain $m = 0x6162$ which is the correct result.\\

This specific lattice works to find roots up to size $N^{\frac{1}{6}}$, so the same construction will work if we want to find

\begin{itemize}
    \item \textasciitilde 170 unkown bits of message from an RSA 1024-bit modulus
    \item \textasciitilde 341 unkown bits of message from an RSA 2048-bit modulus
    \item \textasciitilde 683 unkown bits of message from an RSA 4096-bit modulus
\end{itemize}

If you want to find bigger root you need to create a bigger lattice with more polynomials generated with \ref{eq:create_pol},
this method is better described in TODO, but the principles are the same.
